Optimisation Methods in Business Analytics

### 2020-12-02 optim/opt-talk/insofe.tex
Spell check

\begin{frame}
\frametitle{Some more examples of LP}
\begin{itemize}
\item We are given a lorry with a certain capacity in terms of the weight it 
can carry. We are also given a set of items. Each item has a weight, a value 
and a quantity. The quantity is the number of items of that kind. Fill the 
lorry with a selection of items such that the value is maximized. (Knapsack
problem)

@@

\begin{frame}
\frametitle{Beyond LP}
\begin{itemize}
\item When the objective function is a quadratic form we have the quadratic 
programming problem. Used in portfolio optimisation.
\item Even OLS regression is an optimisation problem.
\item Logistic regression uses MLE solved by an optimiser.
\item Gradient descent, Adaptive gradient descent, congugate gradient descent,
xgboost are all optimisation algorithms used in ML algorithms. All of them 
minimize an error term.
\item Several optimisation algorithms are inspired by nature. For example,
simulated annealing, genetic algorithms, swarm-based algorithms etc.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{To sum up ...}
\begin{itemize}
\item Optimisation mimicks human thinking; no surprise that so many AI
algorithms use optimisation underneath;
\item The boundary between easy and hard problem is determined by convexity;
\item Linear programming is far more pervasive than we sometimes imagine.
\end{itemize}
\end{frame}
\end{document}

>>>>

\begin{frame}
\frametitle{Some more examples of LP}
\begin{itemize}
\item We are given a lorry with a certain capacity in terms of the weight it 
can carry. We are also given a set of items. Each item has a weight, a value 
and a quantity. The quantity is the number of items of that kind. Fill the 
lorry with a selection of items such that the value is maximised. (Knapsack
problem)

@@

\begin{frame}
\frametitle{Beyond LP}
\begin{itemize}
\item When the objective function is a quadratic form we have the quadratic 
programming problem. Used in portfolio optimisation.
\item Even OLS regression is an optimisation problem.
\item Logistic regression uses MLE solved by an optimiser.
\item Gradient descent, Adaptive gradient descent, conjugate gradient descent,
xgboost are all optimisation algorithms used in ML algorithms. All of them 
minimise an error term.
\item Several optimisation algorithms are inspired by nature. For example,
simulated annealing, genetic algorithms, swarm-based algorithms etc.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{To sum up ...}
\begin{itemize}
\item Optimisation mimics human thinking; no surprise that so many AI
algorithms use optimisation underneath;
\item The boundary between easy and hard problem is determined by convexity;
\item Linear programming is far more pervasive than we sometimes imagine.
\end{itemize}
\end{frame}
\end{document}
